Plot density of imputations

### 2020-03-05 4.ShinyMICE/plot_imputation_densities.Rmd
restructure non-conv branch to merge into master

@@

  # plot density of imputed values
  imputed_values <-
    mids[["imp"]]$bmi %>% mutate(case = row_number()) %>%  tidyr::gather("imp", "value", 1:M) %>% .[order(.$case, .$imp),] #%>% group_by(case) %>% mutate(case_mean = mean(value)) %>% ungroup()
  distr[[it]] <-
    case_mean <-
    imputed_values %>% group_by(case) %>% summarise(mu = mean(value), sigma = sd(value))

@@

# or with ggplot to put them in 1 plot
sd_per_case_per_it <-
  purrr::map(1:9, function(x)
    purrr::map_dbl(distr, ~ {
      .$sigma[.$case == x]
    })) %>% as.data.frame() %>% mutate(nr_it = row_number())

colnames(sd_per_case_per_it) <- c(1:9, "nr_it")

#sd_per_case_per_it %>%  tidyr::gather("case", "sd", 1:9) %>% ggplot() + geom_line(aes(x = nr_it, y = sd)) + facet_wrap(~case)
sd_per_case_per_it %>%  tidyr::gather("case", "sd", 1:9) %>% ggplot(aes(x = nr_it, y = sd, col = case)) + geom_point() + geom_smooth(se = F)

>>>>

#### hetzelfde met case nrs omgedraaid!

@@

  # plot density of imputed values
  imputed_values <-
    mids[["imp"]]$hgt %>% mutate(case = row_number()) %>%  tidyr::gather("imp", "value", 1:M) %>% .[order(.$case, .$imp),] #%>% group_by(case) %>% mutate(case_mean = mean(value)) %>% ungroup()
  distr[[it]] <-
    case_mean <-
    imputed_values %>% group_by(case) %>% summarise(mu = mean(value), sigma = sd(value))

@@

n_cases <- max(distr[[1]]$case)
# or with ggplot to put them in 1 plot
sd_per_case_per_it <-
  purrr::map(1:n_cases, function(x)
    purrr::map_dbl(distr, ~ {
      .$sigma[.$case == x]
    })) %>% as.data.frame() %>% mutate(nr_it = row_number())

colnames(sd_per_case_per_it) <- c(1:n_cases, "nr_it")

#sd_per_case_per_it %>%  tidyr::gather("case", "sd", 1:9) %>% ggplot() + geom_line(aes(x = nr_it, y = sd)) + facet_wrap(~case)
sd_per_case_per_it %>%  tidyr::gather("case", "sd", 1:n_cases) %>% ggplot(aes(x = nr_it, y = sd, col = case)) + geom_point() + geom_smooth(se = F)

############# means
# or with ggplot to put them in 1 plot
mean_per_case_per_it <-
  purrr::map(1:n_cases, function(x)
    purrr::map_dbl(distr, ~ {
      .$mu[.$case == x]
    })) %>% as.data.frame() %>% mutate(nr_it = row_number())

colnames(mean_per_case_per_it) <- c(1:n_cases, "nr_it")

#sd_per_case_per_it %>%  tidyr::gather("case", "sd", 1:9) %>% ggplot() + geom_line(aes(x = nr_it, y = sd)) + facet_wrap(~case)
mean_per_case_per_it %>%  tidyr::gather("case", "mean", 1:n_cases) %>% ggplot(aes(x = nr_it, y = mean, col = case)) + geom_point() + geom_smooth(se = F)
